Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-28 ltx/data_paper/DataPaper.tex
edits to discussion and conclusion

Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
\section{Conclusion}
In this chapter, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.  It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified. This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process. In addition to the connectivity kernel weights, synaptic parameter, observation noise and disturbance variances were also identified. The empirical distributions of the estimated non-kernel parameters showed small bias with very smalll standard deviations.

>>>>

Since the non-linearity is a sigmoid function first-order Taylor linearisation provides a good approximation to the lower bound of the likelihood function, however in general settings with more complicated non-linear behaviours higher order terms might need to be included, this however introduces intractable computational complexity.
\section{Conclusion}
In this paper, a method has been developed to estimate a spatially continuous neural field model from electrophysiological data where the kernel spatial support and the field disturbance characteristics were unknown to the estimator.  It was shown that by choosing the synaptic parameter and the observation noise variance within a plausible range these unknown quantities can be identified. This improves the complexity and the accuracy of the EM algorithm by reducing the number of unknown variables in the estimation process. In addition to the connectivity kernel weights, synaptic parameter, observation noise and disturbance variances were also identified. The empirical distributions of the estimated non-kernel parameters showed small bias with very smalll standard deviations.
